---
title: "child2"
format: docx
editor: visual
---

# Examples for quick reference

## Tables

Tables may be in a huxtable object for "seamless" word processing. The resulting table is ugly.

 \

```{r}

# generating the table which is comp.expensive for some reason
tab <- datachunk %>%
  dplyr::select(!(species_no)) %>%
  gtsummary::tbl_summary(
    by = species_char
  )

tab %>%
  as_hux_table()

```

 \

Having a custom ref. docx file, I played around with the formatting and cooked up something passable. Its not modifiable however.

 \

```{r}
#| df-print: kable
#| tbl_colwidths: auto

data(cars)



tab <- cars  %>%
    huxtable::as_hux() %>%
    huxtable::theme_compact() 

huxtable::font_size(tab) <- 6

(tab)



```

 \

You *will* face an issue where a package outputs a "marvellously formatted" html table which would be horrible for your use case. That is a promise, but don't know how to handle it.

 \

```{r}

mod <- lm(petal_width ~ species_char + petal_length, datachunk)

sjPlot::tab_model(mod)


```

 \

Plots are nothing fancy.

 \

```{r}

ggstatsplot::ggbetweenstats(datachunk, 
                            species_char,
                            petal_width,
                            results.subtitle = FALSE) +
  theme_bw()

```

 \

Text outputs; prints computationally intensive output loaded at the beginning.

 \

```{r}

cat(pi_estimate)

```
